Learning constraints in tabular data

### 2016-05-27 Paper/ECAI/tabular.tex
improved the references

First, it borrows techniques from logical and relational learning \cite{luc_book}, as it finds
constraints in multiple relations (or tables). However, unlike typical logical and relational learning
approaches, it focuses on data in spreadsheets and on constraints that can be column or row-wise.
Furthermore, it derives a set of simple “atomic” constraints rather than a set of rules that each consist of multiple literals as in clausal discovery \cite{claudien,Llalouet}. Still several ideas from logical and relational learning
proved to be useful, such as the use of a canonical form, a refinement graph, and pruning for redundancy.
Also related to this line of research is the work on deriving constraints in databases such as functional and multi-valued dependencies \cite{savnik, Mannila-Raiha}
although this line of research has focused on more specialized techniques for specific types of constraints. Furthermore, the constraints used
in spreadsheets are often quite different than those in databases.

>>>>

First, it borrows techniques from logical and relational learning \cite{luc_book}, as it finds
constraints in multiple relations (or tables). However, unlike typical logical and relational learning
approaches, it focuses on data in spreadsheets and on constraints that can be column or row-wise.
Furthermore, it derives a set of simple “atomic” constraints rather than a set of rules that each consist of multiple literals as in clausal discovery \cite{claudien,lallouet}. Still several ideas from logical and relational learning
proved to be useful, such as the use of a canonical form, a refinement graph, and pruning for redundancy.
Also related to this line of research is the work on deriving constraints in databases such as functional and multi-valued dependencies \cite{savnik, Mannila-Raiha}
although this line of research has focused on more specialized techniques for specific types of constraints. Furthermore, the constraints used
in spreadsheets are often quite different than those in databases.
